
\definecolor{PROGRESS}{cmyk}{0.10, 0.10, 0.0, 0.0, 1.00}
\definecolor{TODO}{cmyk}{0.0, 0.10, 0.10, 0.00, 1.00}
\definecolor{DONE}{cmyk}{0.10, 0.0, 0.10, 0.0, 1.0}


\newcommand{\REVIEW}[3]{
  \begin{tcolorbox}[colback={#1}]
    {\bf {#1}. {#2}}
 \end{tcolorbox}
  \begin{quote}
    {#3}
  \end{quote}
}


\REVIEW{TODO}{Equations (1-6): need punctuations; merge them with the last sentence; explain the notations (the text following the equations) either before the equations or use a where clause. Make sure every notation is explained before you close with a period.}{Punctuations has been added and for ease of explanation, an introduction to the notations has been introduced, as well as a where statement for further explanation.}

\REVIEW{DONE}{Table 2: remove the vertical lines.}{The vertical lines were removed.}

\REVIEW{DONE}{Table 3/4: no need for 7 decimal places; four is sufficient; keep the same number of decimal places for the same column}
{Tables have been changed accordingly.}

\REVIEW{PROGRESS}{Bibtex: use full journal names; check for capitalization's (e.g., u.s. should be \{U.S.\}); check for missing volume/page numbers.}{U.S. has been capitalized, all titles have now capital words but we do not use brackets to force capitalization. COVID-19 is now capitalized. Journals are no longer abbreviated.

NEED: go through each individual ref and check.}

\REVIEW{DONE}{Lines 366-379: the two paragraphs listing prediction models are redundant because the same information has already been presented in Figures 4 and 5. They are really just wasting space. The authors should consider removing these two paragraphs, and note in the captions of Figures 4 and 5 that the x-axis labels correspond to the order of models for minimum model error.}{The paragraphs have been removed and the explanation about the sort order was added to the figure captions.}
